---
title: "Data Descriptives"
output: html_notebook
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      error = FALSE, 
                      message = FALSE)
```

```{r, include = FALSE}
# packages
pacman::p_load(tidyverse, readxl, openxlsx, RDS, scales, knitr, kableExtra,
               grid, gridExtra, patchwork, ggpubr, lubridate, plyr, ggridges,
               vtable)

# directories
wd = "/Users/janinedevera/Documents/School/MDS 2021-2023/Thesis/multilabel-legal-text-classification-CIA"
pathdata = paste0(wd, "/data")

# chart template
charts.theme <- theme(axis.title.y.left = element_text(size = 12, margin = margin(r = 15)),
                      axis.title.y.right = element_text(size = 12, margin = margin(l = 15)),
                      axis.title.x = element_text(size = 12, margin = margin(t = 15)),
                      #axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
                      axis.text.x = element_text(size = 12),
                      axis.text.y = element_text(size = 12),
                      axis.ticks = element_blank(),
                      #axis.line.x = element_line("black", size = 0.5), 
                      #axis.line.y = element_line("black", size = 0.5),
                      axis.line.x = element_line("transparent", size = 0.5), 
                      axis.line.y = element_line("transparent", size = 0.5),
                      panel.border = element_rect(color = "#a3a3a3", fill = "transparent"),
                      panel.background = element_rect(fill = "white", color = "white"),
                      #panel.grid.major = element_line(color = "white"),
                      #panel.grid.minor = element_line(color = "white"),
                      panel.grid.major = element_line(color = "#d4d4d4", linetype = "dotted"),
                      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
                      plot.subtitle = element_text(size = 10, face = "italic", hjust = 0.5, margin = margin(b = 15)),
                      legend.position = "bottom",
                      legend.box = "vertical",
                      legend.box.margin = margin(b = 15),
                      legend.margin = margin(r = 10),
                      legend.background = element_rect(fill = "transparent"),
                      legend.spacing.x = unit(0.4, "cm"),
                      legend.key = element_blank(),
                      legend.title = element_blank(),
                      legend.text = element_text(size = 12),
                      plot.caption = element_text(size = 9, hjust = 0, face = "italic"),
                      strip.background = element_rect(fill = "transparent"),
                      strip.text = element_text(size = 12))
```

```{r, include = FALSE}
text <- read.csv(paste0(pathdata, "/01 legal_texts_pipeline_stopwords.csv"))
text_labeled <- read.csv(paste0(pathdata, "/01 legal_texts_with_labels_grouped.csv"))
defs <- read.csv(paste0(pathdata, "/02 oecd_definitions_stopwords_grouped.csv"))
```

## I. LEGAL TEXT

### Distribution of paragraph lengths
```{r}
# combined dataframe
text_labeled <- text_labeled %>% 
  mutate(country = "BR") %>% 
  select(Law, country, Text)

text <- text %>% 
  select(file_name, country, text) %>% 
  dplyr::rename(Law = file_name, Text = text)

combined <- rbind(text_labeled, text) %>% 
  dplyr::distinct(Text, .keep_all = TRUE) %>% 
  mutate(word_count = str_count(Text, "\\w+"))
  
```

```{r}
# number of unique legislation 
combined %>% select(Law) %>% distinct() %>% nrow()
```

```{r}
# number of unique paragraphs 
combined %>% select(Text) %>% distinct() %>% nrow()
```


```{r}
# number of unique labeled legislation 
text_labeled %>% select(Text) %>% distinct() %>% nrow()
```

```{r}
# number of laws by country
combined %>%
  distinct(country, Law) %>%
  group_by(country) %>%
  dplyr::summarise(count = n())
```

```{r}
# number of paragraphs with word count > 500 
combined %>% filter(word_count >= 500) %>% nrow()
```

```{r}
# word count summary stats
summary(combined$word_count)
```


```{r}
plotA1 <- ggplot(combined %>% filter(word_count < 1000), aes(x = word_count)) +
    geom_histogram(fill = "#0C6291") + 
    #geom_bar(aes(fill = depth), width = 0.5, stat = "identity", position = "dodge") +
    charts.theme + 
    xlab("Length") +
    ylab("Count") +
    #scale_x_continuous(limits = c(0,80), breaks = c(0, 10, 20, 30 , 40, 50, 60, 70, 80)) +
    theme(axis.text.x = element_text(size = 12, angle = 0, vjust = 0.5),
          panel.grid.major.x = element_line(color = "#d4d4d4", linetype = "dotted")) +
    labs(#title = "Distribution by Length of Paragraph",
         #subtitle = "corpus of 175 pieces of legislation",
         caption = "For visualization purposes outliers with > 1000 words have been removed.")
plotA1

ggsave(filename="plotA1.png", plot=plotA1, device="png", 
       path=paste0(wd, "/charts"), width = 10, height = 6)
```

```{r}
text %>% select(file_name) %>% unique() %>% nrow()
```

```{r}
laws <- text %>% 
  group_by(file_name) %>%
  dplyr::summarise(counts = n()) %>% 
  mutate(law = str_replace(file_name, "^[A-Z]{2}_", ""),
         country = str_extract(file_name, "^[A-Z]{2}"))
```

### Lengths of laws 
```{r}
plotA2 <- ggplot(laws %>% filter(counts < 500), aes(x=fct_reorder(law, counts), y=counts, label=country)) +
  geom_point(stat='identity', fill="black", size=3, aes(color = country))  +
  geom_segment(aes(y = 0, 
                   x = law, 
                   yend = counts, 
                   xend = law, 
                   color = country),
               size = 1) +
  charts.theme + 
  xlab("") +
  ylab("") +
  scale_color_manual(values = c("#3F5AAB", "#FF781F")) + 
  #scale_y_continuous(labels = label_percent(accuracy = 1L)) + 
  labs(title = "Length of Laws",
       subtitle = "number of paragraphs",
       caption = "For visualization purposes outliers with > 500 paragraphs have been removed.") +
  coord_flip()
plotA2

ggsave(filename="plotA2.png", plot=plotA2, device="png", 
       path=paste0(wd, "/src/R/charts/"), width = 10, height = 8)
```

### Distribution of legislation length 
```{r}
plotA3 <- ggplot(laws %>% filter(counts < 500), aes(x = counts)) +
    geom_histogram(fill = "#FF781F", bins = 8) + 
    #geom_bar(aes(fill = depth), width = 0.5, stat = "identity", position = "dodge") +
    charts.theme + 
    xlab("Length") +
    ylab("Count") +
    #scale_x_continuous(limits = c(0,80), breaks = c(0, 10, 20, 30 , 40, 50, 60, 70, 80)) +
    theme(axis.text.x = element_text(size = 12, angle = 0, vjust = 0.5),
          panel.grid.major.x = element_line(color = "#d4d4d4", linetype = "dotted")) +
    labs(title = "Distribution by Length of Laws",
         subtitle = "Legislation from Philippines and Singapore",
         caption = "For visualization purposes outliers with > 500 paragraphs have been removed.")
plotA3

ggsave(filename="plotA3.png", plot=plotA3, device="png", 
       path=paste0(wd, "/src/R/charts/"), width = 10, height = 6)
```

### Summary table 
```{r}
paras <- laws %>% 
  group_by(country) %>%
  dplyr::summarise('# paras' = sum(counts))
paras

lgs <- laws %>% 
  group_by(country) %>%
  dplyr::summarise('# laws' = n())
lgs

min <- laws %>% 
  group_by(country) %>%
  dplyr::summarise('min length' = min(counts))
min 

max <- laws %>% 
  group_by(country) %>%
  dplyr::summarise('max length' = max(counts))
max 

summary <- plyr::join_all(list(lgs, paras, min, max), by = 'country', type = 'full')
summary
```

## II. LABEL DEFINITIONS 

### Distribution of paragraph lengths
```{r}
plotB1 <- ggplot(defs, aes(x = length)) +
    geom_histogram(fill = "#FF781F", bins = 11) + 
    charts.theme + 
    xlab("Length") +
    ylab("Count") +
    theme(axis.text.x = element_text(size = 12, angle = 0, vjust = 0.5),
          panel.grid.major.x = element_line(color = "#d4d4d4", linetype = "dotted")) +
    labs(title = "Distribution by Length of Paragraph",
         subtitle = "OECD Definitions of Competition Restrictions")
plotB1

ggsave(filename="plotB1.png", plot=plotB1, device="png", 
       path=paste0(wd, "/src/R/charts/"), width = 10, height = 6)
```

### Lengths of definitions
```{r}
plotB2 <- ggplot(defs %>% filter(Sub_Cat != ""), aes(x=fct_rev(Sub_Cat), y=length, label=Main_Cat)) +
  geom_point(stat='identity', fill="black", size=3, aes(color = Main_Cat))  +
  geom_segment(aes(y = 0, 
                   x = Sub_Cat, 
                   yend = length, 
                   xend = Sub_Cat, 
                   color = Main_Cat),
               size = 1) +
  charts.theme + 
  xlab("") +
  ylab("") +
  scale_color_manual(values = c("#24439F","#FF781F", "#24439F","#FF781F")) + 
  #scale_y_continuous(labels = label_percent(accuracy = 1L)) + 
  labs(title = "Length of OECD Definitions",
       subtitle = "number of words") +
  guides(color = FALSE) + 
  coord_flip()
plotB2

ggsave(filename="plotB2.png", plot=plotB2, device="png", 
       path=paste0(wd, "/src/R/charts/"), width = 10, height = 8)

```

## III. BASELINE SCORES 
```{r}
scores_legal <- read.csv(paste0(pathdata, "/scores/01 sim_scores_glove_labeled.csv"))
scores_glove <- read.csv(paste0(pathdata, "/scores/01 sim_scores_legalw2v_labeled.csv"))
```

```{r}
scores_legal_long <- scores_legal %>% 
  pivot_longer(cols = A:D,
               names_to = "category",
               values_to = "simscore") %>% 
  mutate(main_category = substring(category, 1, 1))
```

### Distribution of similarity scores (GloVe)
```{r}
plotC1 <- ggplot(scores_legal_long %>% filter(!(category %in% c("A", "B", "C"))), 
                 aes(y = as.numeric(simscore), x = category)) +
    geom_hline(yintercept = 0.7, color = "#787878") +
      geom_hline(yintercept = 0.5, color = "#787878") +
    geom_violin(aes(fill = main_category)) + 
    charts.theme + 
    xlab("Category") + 
    ylab("Similarity Score") +
    scale_fill_manual(values = c("#95101E", "#F1711B", "#FFE15D", "#234075")) + 
    scale_y_continuous(limits = c(0.2, 0.9), breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)) +
    theme(axis.text.x = element_text(size = 12, angle = 0, vjust = 0.5),
          panel.grid.major.x = element_line(color = "#d4d4d4", linetype = "dotted")) +
    labs(title = "Distribution of Similarity Scores",
         subtitle = "Word embeddings from Legal Word2Vec") + 
    guides(fill = FALSE)
plotC1

ggsave(filename="plotC1.png", plot=plotC1, device="png", 
       path=paste0(wd, "/src/R/charts/"), width = 10, height = 6)
```

```{r}
scores_glove_long <- scores_glove %>% 
  pivot_longer(cols = A:D3,
               names_to = "category",
               values_to = "simscore") %>% 
  mutate(main_category = substring(category, 1, 1))
```

### Distribution of similarity scores (LegalW2V)
```{r}
plotC2 <- ggplot(scores_glove_long %>% filter(!(category %in% c("A", "B", "C"))), 
                 aes(y = as.numeric(simscore), x = category)) +
    geom_violin(aes(fill = main_category)) + 
    charts.theme + 
    xlab("Category") + 
    ylab("Similarity Score") +
    scale_fill_manual(values = c("#95101E", "#F1711B", "#FFE15D", "#234075")) + 
    theme(axis.text.x = element_text(size = 12, angle = 0, vjust = 0.5),
          panel.grid.major.x = element_line(color = "#d4d4d4", linetype = "dotted")) +
    labs(title = "Distribution of Similarity Scores",
         subtitle = "Word embeddings from GloVe") + 
    guides(fill = FALSE)
plotC2

ggsave(filename="plotC2.png", plot=plotC2, device="png", 
       path=paste0(wd, "/src/R/charts/"), width = 10, height = 6)
```

### Dim reduced embeddings (Legal W2V)
```{r}
embed_red_legal <- read.csv(paste0(pathdata, "/scores/02 sim_scores_dim_reduced_legal.csv")) %>% 
  mutate(Category = ifelse(Category == "", name, Category),
         Type = ifelse(name %in% c("A", "B", "C", "D"), "Category", "Text"), 
         Desc = ifelse(name == "A", "Range of suppliers",
                 ifelse(name == "B", "Ability to compete",
                  ifelse(name == "C", "Incentive to compete",
                    ifelse(name == "D", "Choices and information", "")))))
```


```{r}
plotC3 <- ggplot(embed_red_legal %>% filter(Category %in% c("A", "B")), aes(x, y, label = Desc)) +
geom_jitter(aes(color = Category, size=Type, alpha = Type, shape = Type)) +
geom_text() +
scale_color_manual(values = c("#007db7", "#fdb515")) +
scale_size_manual(values = c(5, 1.3)) + 
scale_alpha_manual(values = c(1, 0.8)) + 
scale_shape_manual(values = c(18, 16)) + 
charts.theme + 
theme(panel.grid.major = element_line(color = "#d4d4d4"), 
      legend.position = "right") + 
guides(size = FALSE, alpha = FALSE, shape = FALSE, colour = guide_legend(override.aes = list(size=3))) + 
labs(title = "Text and Label Embeddings in 2D Space",
     subtitle = "Word embeddings from Legal Word2Vec")
plotC3

ggsave(filename="plotC3.png", plot=plotC3, device="png", 
       path=paste0(wd, "/charts/"), width = 10, height = 6)
```

### Dim reduced embeddings
```{r}
embed_red_glove <- read.csv(paste0(pathdata, "/scores/02 sim_scores_dim_reduced_glove.csv"))
```

```{r}
plotC4 <- ggplot(embed_red_glove, aes(x, y)) +
geom_point(aes(color = Category, size=Category, alpha = Category, shape = Category)) +
scale_color_manual(values = c("#95101E", "#F1711B", "#FFE15D", "#e660c7", "#8dd2d9")) +
scale_size_manual(values = c(3, 3, 3, 3, 1.5)) + 
scale_alpha_manual(values = c(1, 1, 1, 1, 0.4)) + 
scale_shape_manual(values = c(18, 18, 18, 18, 16)) + 
charts.theme + 
theme(panel.grid.major = element_line(color = "#d4d4d4"), 
      legend.position = "right") + 
guides(size = FALSE, alpha = FALSE, colour = guide_legend(override.aes = list(size=3))) + 
scale_y_continuous(limits = c(-1, 10), breaks = c(0, 2, 4, 6, 8, 10), labels = label_number(accuracy = 1)) + 
scale_x_continuous(limits = c(-1, 10), breaks = c(0, 2, 4, 6, 8, 10), labels = label_number(accuracy = 1)) + 
labs(title = "Text and Label Embeddings in 2D Space",
     subtitle = "Word embeddings from GloVe")
plotC4

ggsave(filename="plotC4.png", plot=plotC4, device="png", 
       path=paste0(wd, "/charts/"), width = 10, height = 6)
```

